Relevance-based Quantization of Scattering Features for Unsupervised Mining of Environmental Audio

### 2018-02-15 paper/structureScene.tex
comment on Figure 3

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/baselines}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering with or without logarithmic compression, as a function of the rank $k$.}
\label{fig:ASS_-1}
\end{center}
\end{figure}

>>>>

\begin{figure}[t]
\begin{center}
\includegraphics[width=\columnwidth]{figures/baselines}
\caption{Acoustic scene similarity retrieval in the DCASE 2013 private dataset: precisions at rank $k$ ($p@k$) obtained for scattering with or without logarithmic compression, as a function of the rank $k$.
\vl{The x-axis label is wrong. precision should be replaced by "rank $k$". The y-axis should be "precision ($p@k$)". It would be good to have the y-axis range from $0\%$ to $100\%$.
The lines should be thicker and follow a color palette of complementary colors (blue vs. orange). The legends should not be abbreviated: scatT -> scattering, mfcc -> MFCC. }}
\label{fig:ASS_-1}
\end{center}
\end{figure}
